pytourr: Interactive Visualization Interface for the tourr Package

### 2024-09-02 manuscript.tex
basic changes

%% almost as usual
\author{Matthias Templ\,\orcidlink{0000-0002-8638-5276}\\ University of Applied Sciences and Arts \\ Northwestern Switzerland \And 
        Second Author\,\orcidlink{0000-0000-0000-0000}\\ Affiliation}
%% \AND can be used instead of \And and starts a new line
\title{Template and Guidelines for Submitting a Manuscript to the Austrian Journal of Statistics}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Matthias Templ, Second Author} %% comma-separated
\Plaintitle{A Capitalized Title: Something about a Topic} %% without formatting
\Shorttitle{A Capitalized Title} %% a short title (if necessary)

@@

Manuscripts submitted without consideration of the AJS style guide will most likely not be forwarded for review, but rejected with the possibility of resubmission.
}
\Keywords{keywords, comma-separated, non-capitalized, \proglang{R}}
\Plainkeywords{keywords, comma-separated, non-capitalized,, R} %% without formatting
%% at least one keyword must be supplied

>>>>

%% almost as usual
\author{Matthias Medl\,\orcidlink{0000-0002-3354-4579}\\ Institute of Statistics \\ BOKU University \\ Vienna \And 
        Dianne Cook\,\orcidlink{0000-0002-3813-7155}\\ Monash Data Futures Institute \\ Monash University \\ Melbourne \And
        Ursula Laa\,\orcidlink{0000-0002-0249-6439}\\ Institute of Statistics \\ BOKU University \\ Vienna}
%% \AND can be used instead of \And and starts a new line
\title{pytourr: Interactive Visualization Interface for the tourr Package}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Matthias Medl, Dianne Cook, Ursula Laa} %% comma-separated
\Plaintitle{pytourr: Interactive Visualization Interface for the tourr Package} %% without formatting
\Shorttitle{pytourr} %% a short title (if necessary)

@@

Manuscripts submitted without consideration of the AJS style guide will most likely not be forwarded for review, but rejected with the possibility of resubmission.
}
\Keywords{interactive visualization, tourr, exploratory data analysis, \proglang{R}, \proglang{python}}
\Plainkeywords{keywords, comma-separated, non-capitalized,, R} %% without formatting
%% at least one keyword must be supplied
